---
name: "Tad Dallas"
position: "Assistant professor, U of South Carolina, Biological Sciences"
www: taddallas.github.io
email: "tad.a.dallas@gmail.com"
github: taddallas
output:
  vitae::moderncv
---


```{r, include=FALSE, echo=FALSE, message=FALSE}
library(knitr)
library(rmarkdown)
library(vitae)

admin=FALSE

```

\vspace{-1cm} 

# Experience 

\begin{itemize}

\item [2022-- :] \textbf{Assistant Professor}, \textit{Dept of Biological Sciences}, University of South Carolina, Columbia, SC

\item [2019--2021:] \textbf{Assistant Professor}, \textit{Dept of Biological Sciences}, Louisiana State University, Baton Rouge, LA

\item [2018] \textbf{Visiting Researcher}, \textit{Department of Mathematics}, International University of Rijeka

\item [2015:] \textbf{Analytics intern}, HP Vertica - Big Data Platform Dev Team. Boston, MA. 

\end{itemize}




# Education 
\begin{center}
\begin{tabular}{cccc}
  Institution & Location & Degree or Position & Completion Date   \\
  \hline
  Truman State University \ \ \ & Kirksville, MO. & Biology. B.Sc. & 2009 \\
  Truman State University \ \ \  & Kirksville, MO. & Biology. M.Sc. & 2010 \\
  University of Georgia & Athens, GA & Ecology Ph.D & 2016\\
  University of California & Davis & Postdoctoral Researcher & 2018\\
  University of Helsinki & Finland & Postdoctoral Researcher & 2019 \\
  \hline
\end{tabular}
\end{center}





# Publications 


```{r echo=FALSE, results='asis', message=FALSE, comment=""}

pubs <- yaml::read_yaml('../../_data/papers.yml')

formatPub <- function(x){
  auth <- sapply(x$authors, function(x){x$name})
  auth <- paste0(auth, collapse=', ')
  if(grepl("<i>", x$title)){
    x$title <- gsub("<i>", "", x$title)
    x$title <- gsub("</i>", "", x$title)

#    x$title <- gsub("<i>", "\\textit{", x$title)
#    x$title <- gsub("</i>", "}", x$title)
  }
  return(paste0(c("\\item ", 
        auth, '. \\textbf{', x$date,'}. ', x$title, '.  \\textit{',x$journal, '} '), 
          collapse='')
        )
}


cat('\\begin{enumerate}')
for(i in 1:length(pubs)){
  cat(formatPub(pubs[[i]]))
}
cat('\\end{enumerate}')

# noquote(sapply(pubs, formatPub))

```







# Software 

```{r echo=FALSE, results='asis', message=FALSE}
soft <- read.csv('data/software.csv')
soft <- as.data.frame(soft)

soft$Description <- paste(soft$Description, ' (', soft$Location, ')', sep='')
brief_entries(soft,
    when = Name, 
    with = Description
  ) 
  
```




# Presentations 


```{r echo=FALSE, results='asis', message=FALSE}
prez <- read.csv('data/presentations.csv')
prez <- as.data.frame(prez)
prez$Title <- paste(prez$Title, ' (', prez$Location, ')', sep='')
prez$Host <- paste('Hosted by ', prez$Host, '.', sep='')
prez$Host[which(prez$Host == "Hosted by .")] <- ' '

vitae::brief_entries(data=prez, 
  what = Title, 
  when = Date,
  with = Host) |> 
  arrange(desc(when))

```






# Teaching 

```{r echo=FALSE, results='asis', message=FALSE}

teaching <- read.csv('data/teaching.csv')
teaching$students <- paste(teaching$students, 'students')

vitae::brief_entries(data=teaching, 
  what = course, 
  when = year,
  with = students) |> 
  arrange(desc(when))


```







# Funding 

```{r echo=FALSE, results='asis', message=FALSE}
funding <- read.csv('data/grants.csv')
funding <- funding[which(funding$funded==1),]
funding$End[which(is.na(funding$End))] <- '   '
funding$DateRange <- paste(funding$Start, '-', funding$End, sep='')
if(admin){
  funding$totalMoney <- paste('$', funding$Amount, ' ($', trimws(funding$AmountToMe), ')', sep='')
}else{
  funding$totalMoney <- paste('$', funding$Amount, sep='')
}


vitae::detailed_entries(data=funding,  
  what = Name, 
  when = DateRange,
  where= Funding, 
  with = totalMoney)  |> 
  arrange(desc(when))

```





# Academic service

```{r echo=FALSE, results='asis', message=FALSE}
service <- read.csv('data/service.csv')
service$End[which(is.na(service$End))] <- '   '
service$DateRange <- paste(service$Start, '-', service$End, sep='')


vitae::brief_entries(data=service,  
  with = Description, 
  when = DateRange,
  what= trimws(Organization)) |> 
  arrange(desc(when))


```

# Community engagement 

```{r echo=FALSE, results='asis', message=FALSE}

community <- read.csv('data/community.csv')
community$End[which(is.na(community$End))] <- '   '
community$DateRange <- paste(community$Start, '-', community$End, sep='')


vitae::brief_entries(data=community,  
  with = Description, 
  when = DateRange,
  what= Organization)|> 
  arrange(desc(when))

```




# Mentoring 

```{r echo=FALSE, results='asis', message=FALSE}

mentoring <- read.csv('data/mentoring.csv')
mentoring$End[which(is.na(mentoring$End))] <- '   '
mentoring$DateRange <- paste(mentoring$Start, '-', mentoring$End, sep='')
mentoring$Type <- paste(mentoring$Type, ' (', mentoring$Location, ')', sep='')

vitae::brief_entries(data=mentoring,  
  what = Student, 
  when = DateRange,
  with= Type)|> 
  arrange(desc(when))

```


# Undergraduate research
```{r echo=FALSE, results='asis', message=FALSE}

ugmentoring <- read.csv('data/undergrads.csv')
ugmentoring$End[which(is.na(ugmentoring$End))] <- '   '
ugmentoring$DateRange <- paste(ugmentoring$Start, '-', ugmentoring$End, sep='')
ugmentoring$Major <- paste('(', ugmentoring$Major,')', sep='')

vitae::brief_entries(data=ugmentoring,  
  what = Student, 
  when = DateRange,
  with= Major) |> 
  arrange(desc(when))

```





```{r echo=FALSE, results='asis', message=FALSE}

# awards <- read.csv('data/awards.csv')
# refLetters <- read.csv('refLetters.csv')

```



