---
title: "Tad Dallas"
author: 
includes:
  in_header:
    - \usepackage{lmodern}
output:
  pdf_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
    highlight: tango
    theme: journal    
---

```{r, include=FALSE, echo=FALSE, message=FALSE}

library(knitr)
library(rmarkdown)

```

### About 
Assistant professor, University of South Carolina, Biological Sciences \\

| -- | -- | 
| email | tad.a.dallas@gmail.com |
| website | taddallas.github.io | 
| github  | taddallas | 




### Experience 


\begin{itemize}[label={\quad 9999--9999:}, leftmargin=*, itemsep=0pt]

\item[2022--present:] \textbf{Assistant Professor}, \textit{Department of Biological Sciences}, University of South Carolina, Columbia, SC

\item[2019--2021:] \textbf{Assistant Professor}, \textit{Department of Biological Sciences}, Louisiana State University, Baton Rouge, LA

\item[2018] \textbf{Visiting Researcher}, \textit{Department of Mathematics}, International University of Rijeka

\item[2015:] \textbf{Analytics intern}, HP Vertica - Big Data Platform Dev Team. Boston, MA. 

\end{itemize}




### Education 

\begin{tabular}{cccc}
  Institution & Location & Degree or Position & Completion Date   \\
  \hline
  Truman State University & Kirksville, MO. & Biology. B.Sc. & 2009 \\
  Truman State University & Kirksville, MO. & Biology. M.Sc. & 2010 \\
  University of Georgia & Athens, GA & Ecology Ph.D & 2016\\
  University of California & Davis & Postdoctoral Researcher & 2018\\
  University of Helsinki & Finland & Postdoctoral Researcher & 2019 \\
  \hline
\end{tabular}






### Publications 

Ugh this is dumb!

```{r echo=FALSE, results='asis', message=FALSE}

readyaml 

```








### Software 

```{r echo=FALSE, results='asis', message=FALSE}
software <- read.csv('data/software.csv')

```




### Presentations 


```{r echo=FALSE, results='asis', message=FALSE}
prez <- read.csv('data/presentations.csv')

```






### Teaching 


```{r echo=FALSE, results='asis', message=FALSE}

teaching <- read.csv('data/teaching.csv')


```







### Funding 

```{r echo=FALSE, results='asis', message=FALSE}
funding <- read.csv('data/grants.csv')

```





## Service

### Academic service 

```{r echo=FALSE, results='asis', message=FALSE}
service <- read.csv('data/service.csv')

```

### Community engagement 

```{r echo=FALSE, results='asis', message=FALSE}

community <- read.csv('data/community.csv')

```




### Mentoring 

```{r echo=FALSE, results='asis', message=FALSE}

mentoring <- read.csv('data/mentoring.csv')

```









### Awards 

```{r echo=FALSE, results='asis', message=FALSE}

awards <- read.csv('data/awards.csv')

```



